\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-09-11 jss/article.tex
done

\section[Discussion]{Discussion and Summary} \label{discussion}
\pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Poisson and Binomial hierarchical models. The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``method checking'' functionality to examine repeated sampling properties and test that the method is valid at given hyper-parameter values.

As an alternative to other derivative based estimation methods such as MLE and REML \pkg{Rgbp} provides point and interval estimates of true parameters using the ADM framework. Using the ADM framework in conjunction with the specified choice of priors safeguards from cases of overshrinkage and undercoverage that the aforementioned methods suffer from. % (TODO: need citation).

@@

A benefit of \pkg{Rgbp} is that it produces non-random output and so results can easily be reproduced and compared across studies. In addition to being a standalone analysis tool the package can be used as an aid or a tool in a broader estimation procedure. For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure (such as MCMC) the package can be used as a confirmatory tool to check whether the alternative procedure has been implemented correctly. In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus increasing time to convergence. Note, however, that this is only valid when the same model under both procedures is assumed.

Due to the speed and ease of use \pkg{Rgbp} can be utilized as a method of preliminary data analysis. The results of which may inform the statistician whether a more intensive (in terms of coding and computational time) but more precise method (such as MCMC) should be used. As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.

In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''. For example, in GRIMM the point estimates from the package can be substituted into the marginal distribution \ref{normalmarginal} to check whether the data marginally follow this distribution. If certain modeling assumptions have been violated a more sophisticated model can be assumed and implemented by other means.

>>>>

\section[Discussion]{Discussion and Summary} \label{discussion}
\pkg{Rgbp} is an R package for estimating and validating two-level Gaussian, Binomial and Poisson hierarchical models. The package aims to provide a procedure that is computationally efficient with good frequency properties and includes ``method checking'' functionality to examine repeated sampling properties and to test that the method is valid at specified hyper-parameter values.

As an alternative to other derivative based estimation methods such as MLE and REML, \pkg{Rgbp} provides point and interval estimates of parameters using ADM. Using the ADM approach, with our specified choice of priors, protects from cases of overshrinkage and undercoverage from which the aforementioned methods suffer from. % (TODO: need citation).

@@

A benefit of \pkg{Rgbp} is that it produces non-random output and so results easily can be reproduced and compared across studies. In addition to being a standalone analysis tool the package can be used as an aid in a broader estimation procedure. For example, by checking the similarity of output of \pkg{Rgbp} and that of another estimation procedure (such as MCMC) the package can be used as a confirmatory tool to check whether the alternative procedure has been programmed correctly. In addition, the parameter estimates obtained via \pkg{Rgbp} can be used to initialize a MCMC thus decreasing time to convergence. % Note, however, that this is only valid when the same model under both procedures is assumed.

Due to it's speed and ease of use, \pkg{Rgbp} can be used for as a method of preliminary data analysis. Such results may tell the statistician whether a more intensive (in terms of implementation and computational time) but more precise method (such as MCMC) is needed.

%As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.

In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''. For example, in GRIMM, the point estimates from the package can be substituted into the marginal distribution in (\ref{normalmarginal}) to check whether the data marginally follow this distribution.
